Kit Theory

### 2023-06-21 paper/paper.tex
Update.

  \section{Substitution \& Renamings}
  Our sort-indexed syntax allows us to define substitutions and
  renamings which replace all variables of all sorts simultaneously:

>>>>

  \section{Substitution \& Renamings}
  Working with a sort-indexed syntax allows us to define substitutions and
  renamings which replace all variables of all sorts simultaneously:
